---
title: "Nancy_Assignment4"
output: html_notebook
---

# Q2: Loading Packages  
```{r}
library(tidyverse)
library(ggthemes)
```
# Q3: Loading data 
```{r}
assignment4 = read_csv("a4_data.csv")
```
# Q4: Rows and Columns 
```{r}
nrow(assignment4)
ncol(assignment4)
```
There are 3700 rows and 12 columns in the file.
# Q5: Unique participants and trials
```{r}
assignment4 %>% 
  pull(subject) %>%
  unique()

assignment4 %>%
  group_by(subject) %>%
  count()
```
The file has 38 unique subjects; each subject did 100 trials.
# Q6: Levels of variables
```{r}
# Convert prime_condition into a factor
assignment4 = assignment4 %>% 
  mutate(prime_condition = as.factor(prime_condition),
         state = as.factor(state))
levels(assignment4 %>% pull(prime_condition))
levels(assignment4 %>% pull(state))
```
The "prime condition" variable has 4 levels. The "state" variable has 4 levels.
# Q7: Subsets of Columns
```{r}
# Create a new dataframe that contains only the subject and prime condition column from original dataset
prime_information = assignment4 %>% select(subject, prime_condition)
```
# Q8: Subsets of Rows
```{r}
# Create a new dataframe contains only rows where the prime condition is phonological and accuracy is 1
phonological = assignment4 %>% filter(prime_condition == "phonological" & accuracy == 1)
```
# Q9: Summarizing mean accuracy per subject
```{r}
subject_acc = assignment4 %>%
  group_by(subject) %>%
  summarize(mean_acc = mean(accuracy))
```
# Q10: Summarizing accuracy per prime condition
sd()
```{r}
# Calculate the mean accuracy and standard deviation of accuracy for each prime condition
prime_acc = assignment4 %>%
  group_by(prime_condition) %>%
  summarise(mean_acc = mean(accuracy), sd_acc = sd(accuracy))
```
# Q11: Histogram of subject accuracy
```{r}
subject_acc %>% 
  ggplot(aes(x = mean_acc)) +
  theme_few() + 
  geom_histogram(binwidth = 0.2, position = "identity", fill = "skyblue", color = "blue") + 
  labs(x = "mean accuracy", y = "count", title = "Histogram of mean subject accuracy")
```
# Q12: Bar plot of prime condition
```{r}
prime_acc %>%
  ggplot(aes(x = prime_condition, y = mean_acc)) +
  theme_few() +
  geom_col(fill = "skyblue", color = "blue") + 
  labs(x = "prime condition", y = "mean accuracy", title = "Mean accuracy across prime condition")
```
# Q13: Data interpretation
Phonological primes resulted in the highest accuracy; unrelated primes resulted 
in the lowest accuracy. Both kinds of primes and unrelated primes resulted in
similar accuracy.
# Q14: Summarizing accuracy per prime condition and state 
```{r}
state_prime_acc = assignment4 %>% 
  group_by(prime_condition, state) %>%
  summarize(mean_acc = mean(accuracy))
```
# Q15: Bar plot of prime condition and state
```{r}
state_prime_acc %>%
  ggplot(aes(x = prime_condition, y = mean_acc, fill = state)) + 
  theme_few() + 
  geom_col(position = "dodge") + 
  labs(x = "prime condition", y = "mean accuracy", title = "Mean accuracy across prime condition and reported states")
```



